\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-05-20 paper/ms.tex
add short introductory paragraph in the PSF photometry section

    \subsubsection{Correcting Spacecraft Motion using Lightkurve}
        Spacecraft-induced correlated noise remains one of the greatest hurdles to
        analyzing K2 lightcurves. Many algorithms have been developed to mitigate
        motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
        In \lightkurve, we implement an algorithm based off of the self-flat-field
        (SFF) presented in~\cite{vanderburg14}.

@@

>>>>

    \subsubsection{Correcting Spacecraft Motion using Lightkurve}
        Spacecraft-induced correlated noise remains one of the greatest hurdles to
        analyzing K2 lightcurves. Many algorithms have been developed to mitigate
        motion-dependent artifacts~\cite{vanderburg2014}[CITE K2SC and EVEREST].
        In \lightkurve, we implement an algorithm based off of the self-flat-field
        (SFF) presented in~\cite{vanderburg2014}.

@@

NASA's Kepler and K2 missions have been delivering high-precision time series data
for a wide range of stellar types through the official~\cite{jenkins2010} and community-developed
pipelines~\cite{vanderburg2014, luger2016, aigrain2016}. Although those pipelines have
been extremely successful, they tend to focus on studying isolated targets using simple
aperture photometry and often underperform in crowded fields.
However, crowded fields are frequent in many K2 campaigns and will
be a major characteristic of TESS [ADD CITATION]. Therefore, pipelines that can deal with
crowding in a principled way will play a key role on processing such type of data.
